---
title: "The Prevalence of Chlamydia And Gonorrhea Infections Among Pregnant Women"
author: 
date: "`r Sys.Date()`"
output: html_document
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r  echo=FALSE, message=FALSE, warning=FALSE}
#Load libraries
library(tidyverse)
library(janitor)
```



```{r  echo=FALSE, message=FALSE, warning=FALSE}

setwd("D:/DATA_ABSTRACTS/data")

data <- read.csv("all.csv")
 

data <- data %>% select(-X)

data <- data %>%
  rename(
    delivery_date = deliv_dsstdat_inf1,
    birthoutcome = birth_dsterm_inf1,
    gonorhea=ctng_ng_lborres,
    chlamydia=ctng_ct_lborres,
    gonor_test =ctng_lbperf_2,
    chlam_test= ctng_lbperf_1
    
  )

```



```{r}
data$delivery_date <- dmy(data$delivery_date)
```


```{r}

# Total number of of those who were tested are 161
data <- data%>% filter((data$chlam_test==1&data$gonor_test==1))


```


```{r echo=FALSE}


data <- data %>% mutate(age_group = case_when(
  momage < 30         ~ "Young",       
  momage >= 30 & momage < 60 ~ "Middle-aged", 
  TRUE                 ~ NA_character_ 
))

data <- data %>%
  mutate(birthoutcome = factor(case_when(
    birthoutcome == 1 ~ "Live birth",
    birthoutcome == 2 ~ "Fetal death",
    birthoutcome == 77  ~ "Miscarriages",
    TRUE ~ NA_character_
  ), levels = c("Live birth", "Fetal death","Miscarriages")))

data <- data %>%
  mutate(gonorhea = factor(case_when(
    gonorhea == 0 ~ "Negative", 
    gonorhea == 1 ~ "Positive",
    gonorhea == 2 ~ "Inconclusive",
    TRUE ~ NA_character_
  ), levels = c("Negative", "Positive", "Inconclusive")))



data <- data %>%
  mutate(chlamydia = factor(case_when(
    chlamydia == 0 ~ "Negative", 
    chlamydia == 1 ~ "Positive",
    chlamydia == 2 ~ "Inconclusive",
    TRUE ~ NA_character_
  ), levels = c("Negative", "Positive", "Inconclusive")))



data <- data %>%
  mutate(
    chlamydia_pos = ifelse(chlamydia == 1, 1, 0),
    gonorrhea_pos = ifelse(gonorhea == 1, 1, 0),
    any_infection = ifelse(chlamydia_pos == 1 | gonorrhea_pos == 1, 1, 0)
  )

# # 4. Cross-tab: Any Infection vs Birth Outcome
# data %>%drop_na() %>% 
#   tabyl(gonorhea, birthoutcome) %>%
#   adorn_percentages("row") %>%
#   adorn_pct_formatting()


```


#### Basic Demographics
#### Total number of observations :710 out of 2370 (These are only those that were tested for these infections)


####  Summary of mothers age
```{r }
summary(data$momage)
```

####  Age group of Mothers :Middle-aged (age>=30 years )and Young(age < 30 years)
```{r}
table(data$age_group)

```
####  Count of Birthoutcome
```{r}
table(data$birthoutcome)
```


#### 1. Prevalence of Chlamydia

```{r}

data %>%
  count(chlamydia) %>%
  mutate(Percentage = n / sum(n) * 100) %>%
  rename(Count = n, Chlamydia_Status = chlamydia) %>%
  arrange(desc(Percentage))

```

#### 2. Prevalence of Gonorrhea

```{r}
data %>%
  count(gonorhea) %>%
  mutate(Percentage = n / sum(n) * 100) %>%
  rename(Count = n, gonorhea_Status = gonorhea) %>%
  arrange(desc(Percentage))

```
#### 3. Chlamydia vs Birth Outcome

```{r}

chlamydia_vs_outcome <- data %>%
  filter(!is.na(chlamydia), !is.na(birthoutcome)) %>%
  count(chlamydia, birthoutcome) %>%
  group_by(chlamydia) %>%
  mutate(percent = n / sum(n) * 100)

print(chlamydia_vs_outcome)

```


#### 4. Gonorrhea vs Birth Outcome

```{r}

gonorrhea_vs_outcome <- data %>%
  filter(!is.na(gonorhea), !is.na(birthoutcome)) %>%
  count(gonorhea, birthoutcome) %>%
  group_by(gonorhea) %>%
  mutate(percent = n / sum(n) * 100)

print(gonorrhea_vs_outcome)


```


<!-- ```{r} -->

<!-- # 3. Create combined seroprevalence variable (positive to any) -->
<!-- data <- data %>% -->
<!--   mutate( -->
<!--     any_NC_positive = ifelse(gonorhea == 1 | chlamydia == 1,  -->
<!--       1, 0 -->
<!--     ) -->
<!--   ) -->

<!-- ``` -->


<!-- ```{r} -->
<!-- data <- data %>% mutate( any_NC_positive=factor(case_when( any_NC_positive== 1 ~"Positive",                                           any_NC_positive== 0 ~"Negative", -->
<!-- TRUE ~ NA_character_),levels=c("Positive","Negative"))) -->
<!-- ``` -->



<!-- #### 4. Tabulate Prevalence among pregnant women -->

<!-- ```{r} -->

<!-- # 4. Tabulate prevalence among pregnant women -->
<!-- cat("Overall NCs prevalence among pregnant women:\n") -->

<!-- ``` -->

<!-- #### The count of overall prevalence -->
<!-- ```{r} -->
<!-- print(table(data$any_NC_positive)) -->
<!-- ``` -->

<!-- #### Percentages of the overall seroprevalence(%) -->
<!-- ```{r} -->
<!-- print(round(prop.table(table(data$any_NC_positive)) * 100, 1)) -->
<!-- ``` -->

