---
title: "statistical description of seroprevalence of ZCD (Zika, Chikungunya, Dengue) 
"
author: 
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
#and explore pregnancy outcomes 

#R Script: Seroprevalence of ZCD and Birth Outcomes


# Load required libraries
library(tidyverse)

setwd("D:/DATA_ABSTRACTS/data")

data <- read.csv("all.csv")


data <- data %>% select(-X)



```


### Count of those that were tested for any of these zcd
```{r}
data <- data %>%
  filter(
    zcd_lbperf_1 == 1 |  # zikv igm
    zcd_lbperf_2 == 1 |  # zikv igg
    zcd_lbperf_3 == 1 |  # denv igm
    zcd_lbperf_4 == 1 |  # denv igg
    zcd_lbperf_5 == 1 |  # chkv igm
    zcd_lbperf_6 == 1    # chkv igg
  )

cat("Participants tested for any ZCD tests:", nrow(data), "\n")

```


#### Count of those with complete testing for all

```{r}

data <- data %>%filter(
    zcd_lbperf_1 == 1,  # ZIKV IgM
    zcd_lbperf_2 == 1,  # ZIKV IgG
    zcd_lbperf_3 == 1,  # DENV IgM
    zcd_lbperf_4 == 1,  # DENV IgG
    zcd_lbperf_5 == 1,  # CHKV IgM
    zcd_lbperf_6 == 1   # CHKV IgG
  )

# Count of those with complete testing
cat("Participants tested for ALL ZCD tests:", nrow(data), "\n")

```

```{r}
# 1. Recode test result variables for clarity
recode_test_result <- function(x) {
  factor(x, levels = c(0, 1, 2),
         labels = c("Negative", "Positive", "Inconclusive"))
}
```


```{r}


data <- data %>% mutate(age_group = case_when(
  momage < 30         ~ "Young",       
  momage >= 30 & momage < 60 ~ "Middle-aged", 
  TRUE                 ~ NA_character_ 
))

data <- data %>%
  rename(
    delivery_date = deliv_dsstdat_inf1,
    birthoutcome = birth_dsterm_inf1,
    gonorhea=ctng_ng_lborres,
    chlamydia=ctng_ct_lborres,
    gonor_test =ctng_lbperf_2,
    chlam_test= ctng_lbperf_1
    
  )



data <- data %>%
  mutate(birthoutcome = factor(case_when(
    birthoutcome == 1 ~ "Live birth",
    birthoutcome == 2 ~ "Fetal death",
    birthoutcome == 77  ~ "Miscarriages",
    TRUE ~ NA_character_
  ), levels = c("Live birth", "Fetal death","Miscarriages")))


data <- data %>%
  mutate(
    zikv_igm_result = recode_test_result(zcd_zikigm_lborres),
    zikv_igg_result = recode_test_result(zcd_zikigg_lborres),
    denv_igm_result = recode_test_result(zcd_denigm_lborres),
    denv_igg_result = recode_test_result(zcd_denigg_lborres),
    chkv_igm_result = recode_test_result(zcd_chkigm_lborres),
    chkv_igg_result = recode_test_result(zcd_chkigg_lborres)
  )
```


#### Basic Demographics

```{r}
cat(" Total number of observations:", nrow(data),"(These are only those that were tested for these)", "\n")
```




```{r abbreviation-table, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)

# Create abbreviation table
abbrev_table <- data.frame(
  Abbreviation = c("ZCD", "ZIKV", "DENV", "CHKV", "IgM", "IgG"),
  `Full Meaning` = c(
    "Zika–Chikungunya–Dengue (a combined reference to three viruses)",
    "Zika Virus",
    "Dengue Virus",
    "Chikungunya Virus",
    "Immunoglobulin M ",
    "Immunoglobulin G "
  )
)

# Print as nice table
kable(abbrev_table, caption = "Table: Definitions of ZCD-related Abbreviations")





```

####  Summary of mothers age
```{r }
summary(data$momage)
```

####  Age group of Mothers :Middle-aged (age>=30 years )and Young(age < 30 years)
```{r}
table(data$age_group)

```
####  Count of Birthoutcome
```{r}
table(data$birthoutcome)
```



#### 2.  seroprevalence of each types of ZCD

```{r}

# 2. Calculate seroprevalence of each infection type
calculate_seroprevalence <- function(var) {
  round(prop.table(table(var)) * 100, 1)
}

seroprevalence <- list(
  ZIKV_IgM = calculate_seroprevalence(data$zikv_igm_result),
  ZIKV_IgG = calculate_seroprevalence(data$zikv_igg_result),
  DENV_IgM = calculate_seroprevalence(data$denv_igm_result),
  DENV_IgG = calculate_seroprevalence(data$denv_igg_result),
  CHKV_IgM = calculate_seroprevalence(data$chkv_igm_result),
  CHKV_IgG = calculate_seroprevalence(data$chkv_igg_result)
)

print("Seroprevalence (%):")
print(seroprevalence)
```


####  3.  combined seroprevalence variable (positive to any)

```{r}
# [
#     zcd_zikigm_lborres,
#     zcd_zikigg_lborres,
#     zcd_denigm_lborres,
#     zcd_denigg_lborres,
#     zcd_chkigm_lborres,
#     zcd_chkigg_lborres
# ]


# 3. Create combined seroprevalence variable (positive to any)
data <- data %>%
  mutate(
    any_zcd_positive = ifelse(
      zcd_zikigm_lborres == 1 | zcd_zikigg_lborres == 1 |
        zcd_denigm_lborres == 1 | zcd_denigg_lborres == 1 |
        zcd_chkigm_lborres == 1 | zcd_chkigg_lborres == 1,
      1, 0
    )
  )


data <- data %>% mutate( any_zcd_positive=factor(case_when( any_zcd_positive== 1 ~"Positive",                                           any_zcd_positive== 0 ~"Negative",
TRUE ~ NA_character_),levels=c("Positive","Negative")))

```


#### 4. Tabulate seropositivity among pregnant women

```{r}

# 4. Tabulate seropositivity among pregnant women
cat("Overall ZCD Seroprevalence among pregnant women:\n")

```

#### The count of overall seroprevalence
```{r}
print(table(data$any_zcd_positive))
```

#### Percentages of the overall seroprevalence(%)
```{r}
print(round(prop.table(table(data$any_zcd_positive)) * 100, 1))
```


#### 5. ZCDs  By  birth outcomes

```{r}
```


```{r}

zcd_summary <- data %>%filter(!is.na(data$birthoutcome)) %>% 
  mutate(
    zikv_igm_pos = zcd_zikigm_lborres == 1,
    zikv_igg_pos = zcd_zikigg_lborres == 1,
    denv_igm_pos = zcd_denigm_lborres == 1,
    denv_igg_pos = zcd_denigg_lborres == 1,
    chkv_igm_pos = zcd_chkigm_lborres == 1,
    chkv_igg_pos = zcd_chkigg_lborres == 1
  ) %>%
  group_by(birthoutcome) %>%
  summarise(
    total = n(),
        zikv_igm = paste0(sum(zikv_igm_pos, na.rm = TRUE), " (", round(100 * mean(zikv_igm_pos, na.rm = TRUE), 1), "%)"),
    zikv_igg = paste0(sum(zikv_igg_pos, na.rm = TRUE), " (", round(100 * mean(zikv_igg_pos, na.rm = TRUE), 1), "%)"),
    denv_igm = paste0(sum(denv_igm_pos, na.rm = TRUE), " (", round(100 * mean(denv_igm_pos, na.rm = TRUE), 1), "%)"),
    denv_igg = paste0(sum(denv_igg_pos, na.rm = TRUE), " (", round(100 * mean(denv_igg_pos, na.rm = TRUE), 1), "%)"),
    chkv_igm = paste0(sum(chkv_igm_pos, na.rm = TRUE), " (", round(100 * mean(chkv_igm_pos, na.rm = TRUE), 1), "%)"),
    chkv_igg = paste0(sum(chkv_igg_pos, na.rm = TRUE), " (", round(100 * mean(chkv_igg_pos, na.rm = TRUE), 1), "%)"),) %>% ungroup()


```

```{r}
# View the final table
print(zcd_summary)
```

